Prestige bias in cultural evolutionary dynamics

### 2023-04-30 ms/ms.tex
remove mwf comment
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO MWF thinks the paper is better without this paragraph; if we remove, we should also remove references to it from abstac/intro/discussion
\subsection*{Adaptive success-bias weight}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{DM_validation.pdf}
  \caption{
  \textbf{Numerical validation of the DM approximation.}
  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared them to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}). % TODO what is "them"?? where is being compared??
  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
  \textbf{(B)} The log-likelihood of the DM distribution for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
  Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
  \label{fig:DM_validation}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   Fixation probability does not seem to be effected by variation in success bias weight between individuals. % TODO copiers? or role-models?
    Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
   Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
  Here, population size, $N=1000$; 
  success bias weight is normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon \le 10^{-1}$;  % TODO alpha_j ? alpha_i?
  % TODO not clear if epsilon or epsilon^2 should be written in the inequality: x label says variance but epsilon is standard variation.
  phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Adaptive success-bias weight}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{DM_validation.pdf}
  \caption{
  \textbf{Numerical validation of the DM approximation.}
  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
  \textbf{(B)} The log-likelihood of the DM distribution for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
  Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
  \label{fig:DM_validation}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   Fixation probability does not seem to be affected by variation in success bias weight between role-models.
    Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
   Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
  Here, population size, $N=1000$; 
  success bias weight is normally distributed, $\alpha_j \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon^2 \le 10^{-1}$; 
  phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
\end{figure}
